Bioverse: Origins of Life

### 2023-10-04 src/tex/ms.tex
Some structural comments

One origin-of-life scenario has been refined to the point where the threshold flux has been measured.
The cyanosulfidic scenario has been shown to require a mean flux of at least $ F_\mathrm{NUV, min} = \SI{6.8\pm3.6 e10}{\photons\per\centi\meter\squared\per\second\per\nano\meter}$ integrated from \SIrange{200}{280}{\nano\meter} at the surface in order to function (Rimmer et al. 2018; Rimmer et al. 2021 Astrobiology; Rimmer et al. 2023).
\todo[inline]{SR: This is an interesting number, because it is below what was available on early Earth (so this scenario could have worked on early Earth) but until recently it was below what was thought to be available on habitable zone M-dwarf exoplanets. So it was thought that identification of biosignatures on M-dwarf planets could therefore falsify the cyanosulfidic scenario, with a potential caveat for transient UV from flares. Two recent developments have complicated the picture. First, Rimmer et al. 2018 had an error in their radiative transfer routines. Correcting for this error, early M-dwarfs and highly active M-dwarfs emit enough UV to meet the Rimmer et al. 2018 criterion (Ranjan et al. 2023). Second, a recent publication argues that /all/ estimates of M-dwarf UV are underestimates, and that late M-dwarf stars have similar emission to Sunlike stars (Rekhi et al. 2023). I suspect this is incorrect, because it contradicts a lot of work from e.g. the MUSCLES collaboration and the HAZMAT project, but it's worth keeping an eye on in case it is correct after all.}
We use this threshold value as our baseline case.

@@

\subsection{Nautilus}
\subsection{LIFE} % optional

@@

\subsection{Caveats}
\subsubsection{Atmosphere transmission}
Theoretical work suggests that the atmosphere of prebiotic Earth was largely transparent at near-UV wavelengths with the only known source of attenuation being Rayleigh scattering~\citep{Ranjan2017,Ranjan2017c}.
We thus approximated surface UV flux using top-of-atmosphere fluxes.
This represents a conservative approach, since any planet that fails to meet the irradiance criterion receives even lower near-UV radiation at its surface. \todo[inline]{SUKRIT please specify as neccessary}

>>>>

One origin-of-life scenario has been refined to the point where the threshold flux has been measured.
The cyanosulfidic scenario has been shown to require a mean flux of at least $ F_\mathrm{NUV, min} = \SI{6.8\pm3.6 e10}{\photons\per\centi\meter\squared\per\second\per\nano\meter}$ integrated from \SIrange{200}{280}{\nano\meter} at the surface in order to function (Rimmer et al. 2018; Rimmer et al. 2021 Astrobiology; Rimmer et al. 2023).
\todo[inline]{SR: This is an interesting number, because it is below what was available on early Earth (so this scenario could have worked on early Earth) but until recently it was below what was thought to be available on habitable zone M-dwarf exoplanets. So it was thought that identification of biosignatures on M-dwarf planets could therefore falsify the cyanosulfidic scenario, with a potential caveat for transient UV from flares. Two recent developments have complicated the picture. First, Rimmer et al. 2018 had an error in their radiative transfer routines. Correcting for this error, early M-dwarfs and highly active M-dwarfs emit enough UV to meet the Rimmer et al. 2018 criterion (Ranjan et al. 2023). Second, a recent publication argues that /all/ estimates of M-dwarf UV are underestimates, and that late M-dwarf stars have similar emission to Sunlike stars (Rekhi et al. 2023). I suspect this is incorrect, because it contradicts a lot of work from e.g. the MUSCLES collaboration and the HAZMAT project, but it's worth keeping an eye on in case it is correct after all.}
We use this threshold value as our baseline case.
\todo[inline]{TL: this scenario, the impact trigger, and the redox state are all interrelated and not easily to disentangle (UV scenarios depend on the right redox range at the surface, as do impact scenarios); however we can try to build this into the general debate. instead of having an ``other scnearios'' seciton i would suggest discussing/introducing the redox constraints in the introdcution together iwht planet formation and primordial differentiation processes.}

@@

\subsection{Nautilus}
\subsection{LIFE} % optional
\todo[inline]{TL: please not optional... :) happy to help support this section}

@@

\subsection{Caveats}

\subsubsection{Planetary composition}
\todo[inline]{TL: the three scenarios are very specific in terms of planet composition (== redox state :-) and thermal state, we need to discuss this here }

\subsubsection{Atmosphere transmission}
Theoretical work suggests that the atmosphere of prebiotic Earth was largely transparent at near-UV wavelengths with the only known source of attenuation being Rayleigh scattering~\citep{Ranjan2017,Ranjan2017c}.
We thus approximated surface UV flux using top-of-atmosphere fluxes.
This represents a conservative approach, since any planet that fails to meet the irradiance criterion receives even lower near-UV radiation at its surface. \todo[inline]{SUKRIT please specify as neccessary}
